\subsection{A unified account}
\label{sec:discussion}

The two granularities combine into one account. Distillation in RegressionTM is
predominantly a global reshaping of the learned function, with a localized repair component
that appears only for a sufficiently accurate teacher. This single mechanism resolves the
recurring puzzles above:

\begin{itemize}
  \item \textbf{Why teacher accuracy does not predict benefit
    (Section~\ref{sec:teacher_edge}):} the teacher having more data in the holes is largely
    irrelevant because its correction acts globally, not in the holes---except for the
    conditional in-hole repair that only a good teacher can supply.
  \item \textbf{Why ``more data'' reasoning fails and ``less-is-more'' exists
    (Section~\ref{sec:full_data}):} learning quality is dominated by the dense bulk, where
    most points and most error mass live, not the sparse tail; adding harmful bulk points
    back can hurt without fixing the tail.
  \item \textbf{Why every mode modulates rather than corrects
    (Sections~\ref{sec:sharpener}--\ref{sec:stability}):} a global reshaping scales
    whatever global signal the teacher carries and has no spatial mechanism to selectively
    repair weak regions.
  \item \textbf{Why spacing predicts benefit negatively (Section~\ref{sec:spacing}):} when
    a dataset's error is spacing-governed (heterogeneous), a single global correction
    mismatches the varying local structure and fails; when error is homogeneous, a global
    correction fits.
\end{itemize}

Spacing thus governs absolute difficulty (B1) and which datasets benefit (per-dataset
correlation), but not where within a dataset distillation acts (B2)---the difficulty axis
and the benefit axis are decoupled, joined only by the conditional, good-teacher in-hole
repair (B3). Throughout, the clause-level feedback of the TM was not merely the substrate
but the instrument: because guidance modifies the Type~I/II decision directly, we could
attribute the divergence to the unbounded feedback type, localize benefit to carved
regions, and reason about magnitude sourcing---all in terms of the model's own interpretable
machinery.
