\section{Introduction}
\label{sec:intro}

The Tsetlin Machine (TM)~\cite{granmo2018tsetlin} is a propositional, clause-based
learner whose predictions are assembled from human-readable conjunctions of literals,
offering interpretability that most numeric regressors lack. Its regression variant, the
Regression Tsetlin Machine (RegressionTM)~\cite{abeyrathna2020regression}, predicts a
continuous target from a weighted vote of such clauses. This transparency comes at a cost
familiar to interpretable models: accurately fitting a regression surface generally
requires densely sampled training data, and performance degrades where the input space is
only sparsely covered.

This motivates a data-efficiency question. When training data is scarce or unevenly
distributed, can a better-informed \textit{teacher} model---one trained on more or
better-covered data---guide a data-starved \textit{student} to a better fit? Knowledge
distillation is the standard framing for this question, but distillation for the TM is
under-explored, and the usual output-matching (soft-label) recipe~\cite{hinton2015distilling}
does not obviously map onto the TM's discrete, clause-level learning dynamics.

We take a different route. Rather than matching the teacher's output, we let the teacher
intervene inside the student's training loop, at the exact point where the TM decides how
to reinforce or erode each clause. This makes distillation a modification of the
clause-feedback signal itself, keeping the whole mechanism inside the interpretable
substrate of the model. Our central questions are not only whether such guidance helps,
but when (which datasets), where (which regions of the input space), and why.

We answer these through a sequence of controlled experiments under a masked-distillation
protocol, and arrive at a single unifying account. Our contributions are:

\begin{enumerate}
  \item A family of teacher-guided clause-feedback mechanisms for RegressionTM---a
    same-side error blend, an adaptive per-sample trigger, opposite-side feedback-type
    overrides, and teacher-bounded update magnitudes---all expressed as small, reversible
    modifications to the standard fit loop.
  \item A characterization of these mechanisms as \textit{gain modulation}: each scales
    whatever signal the teacher carries, amplifying a helpful teacher and aggravating an
    unhelpful one, but supplying no signal a poor teacher lacks.
  \item The finding that teacher accuracy does not predict distillation benefit, with a
    clean counterexample: the teacher with the largest standalone accuracy edge produces
    the worst distillation outcome.
  \item A demonstration that a 70\%-data guided student can match, and sometimes exceed, a
    full-data model---the latter on datasets where additional data is actively harmful.
  \item The identification of data spacing/density as the governing variable, and a
    unified account in which distillation is a predominantly global reshaping of the
    learned function, with a localized repair component that appears only for a
    sufficiently accurate teacher.
\end{enumerate}
