\section{Data and Methodology}
\label{sec:method}

\subsection{Datasets}
\label{sec:data}

We evaluate on twelve public regression datasets, drawn from scikit-learn, the UCI Machine
Learning Repository~\cite{uci_repository}, the Sutanoy public regression collection, and a
Kaggle stock-market dataset~\cite{gawlik2016nyse}. They were chosen to decouple two
properties that are usually entangled: how accurate the teacher is, and how the data is
geometrically distributed.

Four datasets serve as anchors for the per-region analysis, selected to span teacher
quality. \textbf{Combined Cycle Power Plant}~\cite{tufekci2014ccpp} (ccpp,
$n\!\approx\!9.6$k) predicts a plant's net electrical output from ambient temperature,
pressure, humidity, and exhaust vacuum; the relationship is nearly linear
($R^2\!\approx\!0.93$), making it the cleanest large set in the panel.
\textbf{Airquality}~\cite{devito2008airquality} ($n\!\approx\!6.9$k) predicts benzene
concentration from metal-oxide gas-sensor responses, and its test points are moderately
unevenly spaced. \textbf{California Housing Prices}~\cite{pace1997california} (california, $n\!\approx\!20.6$k)
predicts median house value from eight census predictors.
\textbf{Energy Efficiency}~\cite{tsanas2012energy} (energy, $n\!=\!768$) predicts a
building's heating load from eight shape parameters.

The remaining eight datasets extend this range in two directions. Four are smaller,
approximately linear sets: \textbf{autompg}, \textbf{realestate}, and the textbook
\textbf{mortality} and \textbf{bloodfat} regressions. The other four are time series whose
test points are concentrated or bimodal in feature space and are therefore unevenly
spaced: \textbf{metro} (hourly interstate traffic volume, the most unevenly spaced set in
the panel), \textbf{beijing} (hourly PM2.5), and \textbf{nyse} and \textbf{nyse\_log}
(next-day trading volume). The raw \texttt{nyse} target is heavy-tailed, spanning roughly
$10^2$ to $10^8$ shares, whereas \texttt{nyse\_log} is its log-transformed, better-behaved
control. Across the twelve datasets the objectives therefore range from smooth physical
outputs to heavy-tailed financial volume and bimodal traffic, so the datasets differ not
only in teacher quality but also in spacing structure, which is the axis this study probes.

All loaders keep numeric features only, drop rows with missing values, and use a fixed
per-dataset train/test split. To keep the CPU-based TM tractable, the four large
time-series sets (each with tens of thousands of rows) are strided down deterministically:
the rows are ordered and every $k$-th row is retained, with $k$ chosen to reach about
$8000$ training rows. Deterministic striding, rather than random sampling, preserves the
original ordering and feature-space coverage of the series.

\subsection{Teacher-guided clause feedback}
\label{sec:tgcf}

The teacher is a RegressionTM that is trained once and then frozen. It is trained on less
heavily masked data than the student: the teacher sees the 20\%-hole training set, whereas
the student sees the more sparsely sampled 30\%-hole set (Section~\ref{sec:protocol}). In
this sense ``less-masked'' means the teacher retains more of the training distribution and
is therefore better informed about the regions the student is missing.

During the student's \texttt{fit}, at each training sample we optionally (with probability
$p_{\text{teacher}}$) use the teacher's prediction to adjust the student's per-sample error
before the Type~I/Type~II dispatch. We call the sign and magnitude of this adjusted error
the teacher's \textit{error signal}, since it is what the teacher contributes to the update.
The adjustment depends on whether teacher and student agree:

\begin{itemize}
  \item If the teacher and student errors lie on the same side of the encoded target, we
    blend the student's error toward the teacher's by a factor $f$ (a ``same-side
    blend''), reinforcing the update in a direction both models agree on.
  \item If they lie on opposite sides, the baseline ignores the teacher there
    ($f_{\text{opposite}}=0$); our variants instead act on these disagreement samples in
    controlled ways.
\end{itemize}

Because the intervention modifies the per-sample error before dispatch, the teacher
influences which feedback type fires and how large the update is, steering the clause-level
learning directly rather than the model output. Every variant reduces exactly to the
unmodified RegressionTM when the teacher is disabled, which we verify by reproducing the
baseline arm identically across experiments.

\subsection{The family of mechanisms}
\label{sec:family}

We develop the mechanisms as a sequence of small, versioned modifications. Each named mode
below is reported as a column in Tables~\ref{tab:adaptive}--\ref{tab:stability}, referenced
here for the reader.

\begin{itemize}
  \item \textbf{Baseline} (\texttt{uniform}, Tables~\ref{tab:adaptive}--\ref{tab:stability}):
    the teacher fires at a fixed probability $p_{\text{teacher}}$ on same-side samples,
    with opposite-side samples ignored. This is the same-side blend and the reference arm
    against which all gains are measured.
  \item \textbf{Adaptive trigger} (\texttt{adapt\_disagree}, \texttt{adapt\_error},
    Table~\ref{tab:adaptive}): rather than firing at a uniform probability, fire the teacher
    preferentially where it is most informative, via a budget-matched per-epoch probability
    $p_e = \operatorname{clip}(p \cdot d_e / \operatorname{mean}(d_e), 0, 1)$, with $d_e$
    either the teacher--student disagreement or the student's error.
  \item \textbf{Opposite-side type override} (\texttt{force\_ii}, \texttt{teacher\_sign},
    Tables~\ref{tab:tmag} and~\ref{tab:stability}): on disagreement samples, override the
    feedback type while keeping the student's error magnitude. \texttt{force\_ii} always
    fires the bounded Type~II, whereas \texttt{teacher\_sign} chooses the type from the sign
    of the teacher's error.
  \item \textbf{Stability fixes} (\texttt{teacher\_sign\_ii}, \texttt{teacher\_sign\_tmag},
    Table~\ref{tab:stability}): two safeguards for \texttt{teacher\_sign}.
    \texttt{teacher\_sign\_ii} removes its Type~I branch, so it applies only the bounded
    Type~II. \texttt{teacher\_sign\_tmag} keeps the type routing but takes the update
    magnitude from the teacher's own prediction error rather than the student's; because the
    teacher is frozen, this magnitude is fixed in advance and cannot grow during training,
    which caps how large any single update can be.
  \item \textbf{Teacher-bounded magnitude} (\texttt{force\_ii\_tmag}, \texttt{sameside\_tmag},
    Table~\ref{tab:tmag}): \texttt{force\_ii\_tmag} combines forced Type~II with the
    teacher-bounded magnitude, while \texttt{sameside\_tmag} leaves the opposite-side branch
    untouched but has the same-side updates take the teacher's magnitude.
\end{itemize}

\subsection{Masked-distillation protocol}
\label{sec:protocol}

To create a controlled scarcity setting, we carve nested structured holes into the training
set using a $k$-NN procedure: the teacher is trained on an 80\%-kept set (a 20\% structured
hole), and the student on a nested 70\%-kept set (a 30\% hole) contained within the
teacher's. The guided student and the unguided baseline train on the same 30\%-hole data,
differing only in whether the teacher is active. All models are evaluated on a fixed,
unmasked held-out test set, which isolates the effect of distillation from any change in the
student's own data.

\subsection{Experimental setup}
\label{sec:setup}

Unless noted, we use $T=5000$, $1000$ clauses, specificity $s=2.75$, same-side blend
$f=0.75$, teacher-firing probability $p_{\text{teacher}}=0.5$, $100$ epochs, and $6$ seeds
(42--47). The teacher and student share these hyperparameters and differ only in their
training data, and the same fixed configuration is used for every dataset and mode, so
reported differences reflect the distillation mechanism rather than per-dataset tuning.
Comparisons are paired by seed. We denote the full-data ($0\%$-hole) model \textbf{M00}, the
teacher ($20\%$-hole) model \textbf{M20}, and the unguided student trained on the
$30\%$-hole data \textbf{M30}. M30 is the baseline against which distillation benefit is
measured: $\texttt{impr} = \mathrm{RMSE}(\text{M30}) - \mathrm{RMSE}(\text{guided})$, with a
positive value meaning distillation helps, reported with paired $t$-statistics across seeds.
Most analyses use the four anchor datasets; the dataset-level correlation study
(Section~\ref{sec:spacing}) uses the full twelve. M00 serves as an upper-reference ceiling
and M20 as the standalone-teacher baseline.
