\section{Results and Discussion}
\label{sec:results}

Throughout, we label each anchor dataset by its \textit{distillation outcome}---whether
guidance helps the student, not how accurate the teacher is in isolation. We call ccpp a
\textbf{good} teacher (guidance helps across all modes), airquality a \textbf{weak} teacher
(marginal help), california a \textbf{neutral} teacher (negligible-to-slightly-harmful),
and energy a \textbf{bad} teacher (guidance consistently hurts). As
Section~\ref{sec:teacher_edge} shows, this ordering does \textit{not} follow the teacher's
standalone accuracy. For scale, the unguided 30\%-hole baseline RMSEs against which the
\texttt{impr} values are measured are $5.20$ (ccpp), $1.74$ (airquality), $0.62$
(california) and $1.22$ (energy); a gain of $+0.40$ on ccpp is thus an $\approx\!8\%$
error reduction.

\subsection{Distillation modulates, rather than corrects, the teacher's signal}
\label{sec:sharpener}

Our first structural finding is that teacher guidance acts as a multiplicative gain on the
teacher's existing effect: it amplifies whatever signal the teacher carries rather than
correcting for the teacher's weaknesses.

\paragraph{Adaptive triggering.}
Concentrating the teacher's action where it disagrees with the student, or where the
student errs, magnifies the outcome in both directions (Table~\ref{tab:adaptive}). On the
good teacher ccpp, \texttt{adapt\_error} yields the single best distillation result in our
study ($+0.496$, $t=4.64$, vs the \texttt{uniform} trigger's $+0.360$). But on the harmful
datasets the same concentration makes things significantly worse (energy
\texttt{adapt\_error} $-0.372$, $t=-5.34$; gain vs \texttt{uniform} $t=-6.25$). The
hoped-for ``focus on disagreement to avoid hurting easy points'' does not occur---on a
bad-teacher dataset the disagreement region is exactly where the teacher is most wrong.

\begin{table}[t]
\centering
\footnotesize
\caption{Adaptive trigger, mean \texttt{impr} (paired, 6 seeds).}
\label{tab:adaptive}
\begin{tabular}{llrrr}
\toprule
dataset & teacher & uniform & adapt\_disagree & adapt\_error \\
\midrule
ccpp       & good    & $+0.360$ & $+0.322$ & $\mathbf{+0.496}$ \\
airquality & weak    & $+0.078$ & $+0.096$ & $+0.147$ \\
california & neutral & $-0.013$ & $-0.029$ & $-0.062$ \\
energy     & bad     & $-0.062$ & $-0.277$ & $\mathbf{-0.372}$ \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Teacher-bounded magnitude.}
The same behavior reappears when the update magnitude is sourced from the teacher. The
cleanest comparison is \texttt{force\_ii} against \texttt{force\_ii\_tmag}
(Table~\ref{tab:tmag}): identical forced Type~II, with only the magnitude source changing
from student to teacher. Sourcing the magnitude from the teacher amplifies the good teacher
(ccpp $+0.251 \rightarrow +0.431$, $t=3.52$, 6/6 seeds---our best good-teacher result) and
caps the bad teacher's harm (energy $-0.237 \rightarrow -0.116$), but it backfires on the
marginal teacher (airquality's $+0.175$ win reverses to $-0.140$). The airquality win came
specifically from using the student's magnitude on disagreement samples; over-trusting a
teacher that is only weakly better erases it. \texttt{sameside\_tmag} tells the same story
from the other side: it is the gentlest mode on the bad teacher (energy $-0.013$,
essentially no harm) yet worsens the neutral california case.

\begin{table}[t]
\centering
\footnotesize
\caption{Effect of teacher-bounded magnitude, mean \texttt{impr}.}
\label{tab:tmag}
\begin{tabular}{llrr}
\toprule
dataset & teacher & \texttt{force\_ii} & \texttt{force\_ii\_tmag} \\
\midrule
ccpp       & good    & $+0.251$ & $\mathbf{+0.431}$ \\
airquality & weak    & $\mathbf{+0.175}$ & $-0.140$ \\
california & neutral & $-0.015$ & $-0.017$ \\
energy     & bad     & $-0.237$ & $-0.116$ \\
\bottomrule
\end{tabular}
\end{table}

The consequence is that no single mode is best everywhere:
\texttt{force\_ii\_tmag}/\texttt{sameside\_tmag} suit a known-good teacher, plain
\texttt{force\_ii} a marginal one, and \texttt{sameside\_tmag}/\texttt{uniform} minimize
harm when the teacher may be bad. Every mechanism scales the teacher's signal; none
supplies signal a bad teacher lacks.
