Regression with the Tsetlin Machine (RegressionTM) offers an interpretable,
logic-based alternative to conventional numeric predictors, but learning an accurate
regression surface typically requires densely sampled training data, raising the
question of how well such models can be trained when data is scarce. In this work, we
study teacher--student knowledge distillation for RegressionTM, asking not merely
whether a frozen, better-informed teacher can improve a data-starved student, but where
and why it does so. We introduce a family of teacher-guided feedback mechanisms that
operate inside the student's training loop: at each training sample, the teacher's
encoded prediction adjusts the student's per-sample error before the Type~I/Type~II
feedback decision, letting the teacher act on the clause-level update rather than on the
output. Building on a simple same-side error blend, we develop and evaluate adaptive
triggering, opposite-side feedback-type overrides, and teacher-bounded update
magnitudes, benchmarking them under a controlled masked-distillation protocol in which
nested structured holes carve progressively sparser training sets. Evaluation is paired
by seed on held-out data across datasets that span the full range of teacher quality.

Our experiments yield several consistent findings. Each correction mechanism scales
whatever signal the teacher carries---amplifying a good teacher and aggravating a poor
one---and none rescues an unhelpful teacher. We establish that a teacher's standalone
accuracy does not predict whether distilling from it helps. Sourcing the update
magnitude from the frozen teacher's bounded error reduces seed-level error variance and
roughly halves the harm of a poor teacher; however, it also erases the benefit of a
marginally helpful one. We further show that a guided student trained on 70\% of the
data can match a model trained on the full data, and can surpass it in settings where
additional data is harmful. Finally, we find that data spacing and density, rather than
teacher accuracy, govern distillation benefit. Distillation in RegressionTM is therefore
a global reshaping of the learned function: it helps when a dataset's error is not
strongly spacing-governed (smooth and homogeneous, so a global correction fits) and
fails when the error is spacing-governed (heterogeneous, so a global correction
mismatches the local structure). A per-test-point analysis shows this reshaping to be
largely global---benefit does not track local spacing---yet reveals that a sufficiently
accurate teacher partially repairs the specific regions whose training support was
removed. Throughout, the clause-level feedback of the TM provides a transparent
mechanism for inspecting and steering what the teacher transfers.
